Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-05-20 Scripts/Initial_Analysis.Rmd
Sensitivity of alternative analysis

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

### ------------ ##
# Select a trshold
selected_tresh <- "tresh_two"
### ------------ ##

@@

  # Weighted verion
  boxplot_data <- Eme_Res %>% 
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    mutate(weight = )
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    )#,
    # For number labels
    # un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

@@

Testing different Per values for the centroids

@@

>>>>

  # Estimate noice from ensemble members
  historic_sd <- Trans_index %>% 
    filter(year <= Hist_y) %>% 
    # Alternative method sensitivity analysis
    group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    # group_by(taxon_key,neighbour_id,ensemble) %>% #Average historic data per year first
    summarise_at(vars("trans_index"),
                 c(trend= mean),
                 na.rm=T
                 ) %>% 
    group_by(taxon_key,neighbour_id) %>% #Capture ensemble variation
    summarise_at(vars("trend"),
                 c(hist_mean=mean,
                   noise=sd,
                   n_ens = ~n())
                 )

@@

### ------------ ##
# Select a treshold
selected_tresh <- "tresh_two"
### ------------ ##

@@

  # Weighted verion
  boxplot_data <- Eme_Res %>% 
    # Get the order of boxes
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>%
    summarise(n_eezs = length(unique(sf_eez_name))) %>%
    # Get the rest of the data
    left_join(Eme_Res) %>%
    filter(tresh == tresh_list[i],
           !is.na(un_sub_region)) %>%
    # mutate(weight = )
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and\nthe Car.",
                                  ifelse(str_detect(un_sub_region,"Australia"),"Aus. and New Z.",
                                         ifelse(str_detect(un_sub_region,"Sub-Saharan"),"Sub-Saharan\nAfrica",
                                                paste(un_sub_region)))
    )#,
    # For number labels
    # un_sub_region = paste(un_sub_region," (n = ",n_eezs,")",sep="")
    )

@@

### Testing different Per values for the centroids

@@

### Noise for all ensemble members

```{r read_raw_data}

# Taxon_list_emer <- list.files(my_path("R",extra_path = "Emergence_2005"))
Taxon_list_emer <- list.files("~/Desktop/Emergence_p95_alt")

# Paths <- paste(my_path("R",extra_path = "Emergence_raw_p95"),Taxon_list_emer,"_emergence_raw.csv",sep="")[1:10]

Paths <- list.files("~/Desktop/Emergence_p95_alt",full.names = T)

# Load all sp in one table
Eme_Alt_Res <- bind_rows(lapply(Paths, fread)) %>% 
  left_join(Neighbours,
            # by = c("eez_name","eez_neighbour")
  ) %>%
  rename(sf_eez_name=eez_name) %>%
  left_join(Matching_names,
            by=  "sf_eez_name") %>%
  clean_names() %>%
  mutate(tresh = str_to_lower(tresh)) %>% 
  rename(emerging_yr = mean_emer)
